Statistical Detection of Collective Data Anomalies

### 2017-10-07 Paper/Template/paper.tex
Version for upload

It is hard to detect a single record that is alerted but still remain in correct value scopes, but if many data records are altered to change a final decision, we can still detect malicious data manipulation behaviours.
		According to our observation, typical data manipulations on numerical data will lead to a drift or distortion of its original distribution. For measurable reshaping, we can enclose data collections with similar distribution patterns and filter out those strangely shaped ones. In this paper, we adopt Jensen-Shannon divergence as the similarity measurement among different distributions. Comparing with a estimated ground truth, each data collection can be mapped into a single real number within a definite interval. Then a gaussian classifier can be applied to detect outliers derived from manipulated data. \textcolor{red}{[This is not clear at all. Why sets == windows? Also the whole paragraph fails to tell a clear story especially what you did and why you did. Moreover, you need to outline your contributions explicitly] To automatically calculate adaptive threshold for the classifier, we keep two evidence sets for both normal points and anomalies, taking advantage of the property provided by Jensen-Shannon divergence. And those evidence sets are set to be slide windows to keep up to the evolving features in dynamic scenarios.}
	The details of our technique are put together with a real world problem of ``Click Farming'' and had been evaluated on both raw and synthetic data sets corresponding to the problem, demonstrating the correctness and effectiveness of the technique.

@@

			Detection approaches can be categorized into three types according to whether data is labeled: \textit{Supervised}, \textit{Semi-Supervised} and \textit{Unsupervised} anomaly detection. As the name suggests, supervised detection methods train models on completely labeled data, while unsupervised detection leverages data without any labeling. Semi-supervised detection approaches train model on data that has labeled instances for only the normal class. Supervised detection is commonly applied when both normal and anomalous data can be obtained~\cite{fujimaki2005approach}. When it comes to the circumstances that anomalous data is hard to obtain or there exist too many types of anomalies to enumerate, semi-supervised or unsupervised approaches are usually taken into consideration.
			To make the final decision, detection algorithms mostly yield a score from each input instance, denoting how likely it is anomalous. An algorithm then selects top few as anomalies or compare the scores with a threshold, or outputs a label on each instance, and then decides whether each label belongs to the normal class.
			Currently, distance based~\cite{cao2014scalable,cao2017multi} and feature evolving algorithms~\cite{masud2013classification,li2015discovery,shao2014prototype} catch most attention. Others adopted tree isolation~\cite{zhang2017lshiforest}, model based~\cite{yin2016model} and statistical methods~\cite{zhu2002statstream} in certain applications.

@@

			A research performed in China showed that 81.9\% of investigated people had heard of the behaviour of click farming, 51.2\% of them had seen \textcolor{red}{people around them click farmed ????}and 18.9\% of them had experience of click farming themselves~\cite{yan2015report}. American researchers reported in 2015 that over 11000 sellers were detected to have click farmed records and only 2.2\% of 4000 investigaed sellers had been penalized because of the cheating attempts~\cite{netease2015research}. \textcolor{red}{in which market?}

@@

			\begin{figure}[ht]
				\centering
				\includegraphics[width=\linewidth]{fig/ExampleCDF.png}
				\caption{Example Cumulative Distribution Function of Original And Click Farmed Daily Transaction Data}
				\label{fig:example-ecdf}
			\end{figure}

@@

	\section{Preliminaries}\label{sec:preliminaries}
		Statistical divergence, also called statistical distance, measures the similarity between two or more distributions.
		Mathematically, statistical divergence is a function which describes the ``distance'' of one probability distribution to the other on a statistical manifold. Let $\mathbb{S}$ be a space of probability distributions, then a divergence is a function from $\mathbb{S}$ to non-negative real numbers\textcolor{red}{wrong! how about 0?}: 
		\begin{equation}
			D(\cdot || \cdot): \mathbb{S} \times \mathbb{S} \rightarrow \mathbb{R^+}
		\end{equation}

@@

	\section{Statistical Detection}\label{sec:algorithm-details}
		Diverse data sets in the real world show certain structures caused by hidden patterns or relationships among records. For example, the traffic volume in the highway and the business transaction records, they may show a relatively stable distribution in the daily scale. Manipulation on those data (e.g. Fig.~\ref{fig:example-ecdf}) results in a drift or distortion of the distribution, which can be captured to trigger an alarm. There are some difficulties in the specific design and implementation of the technique:

@@

			In order to generate an accurate approximation, the step size is the most important parameter the algorithm should determine. If the size is too small then the histogram will be over fitting; but if the size is too large then the estimation will be too coarse to depict the original shape. According to statistics theory, when dealing with a sample size of $k$, a step size of 
			\begin{equation}\label{equ:step-size}
				l = c \sigma k^{-0.2},
			\end{equation}
			which will give a best partition size, where $c$ is a constant relative to the shape of distribution (e.g. for normal distribution, $c=1.05$). For data sets with a large number of elements, a random sampling method, such as Monte-Carlo method, can be applied to speed up the estimation procedure.

@@

			A naive but prevalent approach is to set a fixed value as the threshold. This approach is easy to implement and may give satisfying results in specific cases. However, a fixed threshold requires specific analysis in the certain scenario, manual observation and tuning of parameters, which involves lots of human labour. The rule of ``$3 \sigma$'' \textcolor{red}{need citation or simple explanation here}can be used to automatically determine a threshold. But as a rigid metric, it is merely an estimation of a suitable boundary considering average situations, which is far from optimality when concrete data is provided. It would be either higher than the optimum if anomalous data lies far away from the normal cluster, or lower than the optimum if the anomalies sit close to the cluster centre.

@@

			Fortunately, applying divergence as the distance measurement among data collections provides a fine property. That is, divergences of normal data collections assemble together, forming a quasi-gaussian distribution. And those of anomalies also form a quasi-guassian distribution which lies in the right-hand-side to the other one on the real line. As a result of further observation, however, true distribution of both JSDs derived from normal and anomalous data collections may differ a little more from the standard gaussian than the expected estimation error (Fig.~\ref{fig:jsd-dist}). That is due to the unknown randomness within real world data. Few assumptions can be applied in real world data sets, no mention that data volume is sometimes relatively low. This topic is out of the domain discussed in this paper and we here only introduce the technique instead of the specific distribution model. 
\textcolor{red}{WHAT do you want to say here? This sentence seems weird. However, in the scenarios that better models can be calculated, distributions here can be replaced to produce better results. }
For the simplicity of our proposal, we deem the distributions of JSDs to be gaussian.

@@

			According to E.q.(\ref{equ:linear-weight}), the threshold value can be automatically determined. The optimal threshold will minimize total errors and yield an optimal outcome. \textcolor{red}{The only requirement for this technique is another evidence set containing data point derived from anomalous data collections.}

			However, this is not accurate enough, since equation (\ref{equ:linear-weight}) implicates an assumption that the chances are the same for a new data collection to be either anomalous or not. If we can determine the probability for a new data collection to be anomalous in any segment of data sequence, the equation should be modified as:
			\begin{equation}\label{equ:linear-balanced}
				{\footnotesize
				\begin{split}
					T & = \mathop{\arg\min}_{T} \alpha\int_{0}^{T}PDF_{a}(x)dx +
					(1-\alpha)\int_{T}^{log_k2}PDF_{n}(x)dx\\
					& \approx \mathop{\arg\min}_{T}
					\alpha\int_{0}^{T}
					\frac{e^{-\frac{(x - \mu_a)^2}{2\sigma_a^2}}}{\sqrt{2\pi} \sigma_a}dx
					+ 
					(1-\alpha)\int_{T}^{log_k2}
					\frac{e^{-\frac{(x - \mu_n)^2}{2\sigma_n^2}}}{\sqrt{2\pi} \sigma_n}dx
				\end{split}}
			\end{equation}

			Where $\alpha$ is the anomaly probability. E.q.(\ref{equ:linear-balanced}) is much more complicated. But it can be reduced to a quadratic equation.
			Section~\ref{sec:exp-threshold} compares some estimations for optimal threshold under a real world circumstance. It shows the difference among calculators and that equation(\ref{equ:linear-balanced}) outperforms others when $PDF_n(x)$ and $PDF_a(x)$ are actually gaussian.

		\subsection{Dynamic DCAD}\label{sec:alg-dynamic}
Algorithm~\ref{alg:static} regards every data collection to be sampled from a static environment. That is to say the seller will never change his or her products and customer volumes always remain the same. In most cases, real world data is always in the process of evolution and fluctuation. Online shops are often in the process of expanding or dwindling. Thus the sales distribution will slightly change as time goes on. Therefore, the algorithms should automatically adapt to the trend at any time. To meet the need, a sliding window technique has been applied to the basic algorithm frame work. Thus, considering discussion in section~\ref{sec:alg-histogram} and~\ref{sec:alg-threshold}, a dynamic version is proposed in Algorithm~\ref{alg:dynamic}.

@@

		\begin{enumerate}
			\item How to emulate different types of click farming?
			\item Is the analysis in section~\ref{sec:related-realworld} and~\ref{sec:alg-basic} applicable and accurate in real world data sets.
			\item Is the technique efficient against click farming? And How sensitive will the classifier be confronting different magnitude of click farming?
			\item What is the performance of different adaptive thresholds?
		\end{enumerate}

@@

			Fig.~\ref{fig:daily-transaction-volume} shows the daily transaction volume of the seller. It sees a trend of daily sale which is slightly moving as the time goes. And the daily selling distributions, as is shown in Fig.~\ref{fig:sale-distribution-sample}, display a roughly similar shape.

@@

			To play the role of purchasing platform, we surveillance two levels of transaction distribution. The first level is simply drawing a histogram aligned to time spans. The second level is to draw a histogram on the sub-volumes in each time span. For example, as shown in Fig.~\ref{fig:histogram-example}, the first level histogram can be drawn by counting the number of hourly sales. The frequencies of each bucket in 1st level histogram is: $\mathbb{F}=$\{0, 0, 0, 0, 0, 0, 0, 1, 13, 30, 37, 68, 60, 66, 72, 94, 75, 113, 127, 182, 165, 61, 0, 0\}. Then, counting $\mathbb{F}$ with a step size 20 gives the 2nd level histogram.

@@

			In order to test the performance of Algorithm~\ref{alg:dynamic}, every single collection was fed into the algorithm by time order. Each input collection has a probability of $\alpha$ to be anomalous, namely, click farmed. The algorithm checks each collection with 1st or 2nd level histogram and give an answer of true or false. Several metrics were explored in the following experiments.

@@

			When classifying toward 1st level histograms, centralized click farming behaviours can be easily discovered. As displayed in the left two columns in Fig.~\ref{fig:raw-hist-1st}, normal collections share a similar distribution while centralized click-farmed ones abruptly violates the original shape. However, as a clever click farmer, equalized click farming \textcolor{red}{did not in the least distorted the distribution.} Most of them escape the security check under the perfect disguise.
			But when it comes to 2nd level histograms, the ``clever disguise'' does not work any longer. It can be clearly seen in Fig.~\ref{fig:raw-hist-2nd} that both types of click farming shows an obvious difference from the normal ones, while the normal ones still share a similar distribution.
			From the overview in Fig.~\ref{fig:raw-overview}, the difference between normal and anomalous collections can be observed more intuitively.

		\subsection{Experiment on Synthetic Data}\label{sec:exp-synthetic}
			As is put in the former section, every single record in transaction collections gives only a time stamp aligned at hours. Part of the information was erased with the absence of minutes and seconds. In the following experiments, every time stamp was assigned a random value for minutes and seconds. Therefore, the synthetic data set should be closer to the real world case. Moreover, the step size in the histograms can now be calculated more precisely. In the 1st level histogram, the constant $c$ in E.q.(\ref{equ:step-size}) was set to 0.5 since the PDF of daily distribution was approximately a linear function. And in the 2nd level histogram, sub-volumes of every 300 seconds were counted, producing more data points in the 2nd level data collections. Then, constant $c$ in E.q.(\ref{equ:step-size}) was also set to 0.5 given that the 2nd level histogram was also approximately a linear function.
			We tested algorithm performance for $\alpha \in \{0.1, 0.3, 0.5, 0.7, 0.9\}$, with $\mathbb{E}_N$ and $\mathbb{E}_A$ the same configuration as before. Results are shown in Table~\ref{tab:syn-result-1st} and~\ref{tab:syn-result-2nd}.

@@

			The result shows that the algorithm can efficiently distinguish the normal and anomalous data collections. No matter how much proportion in them is anomalous, the algorithm always gives a high accuracy. That is because the adaptive threshold was designed to minimize the number of total errors, which was not relevant directly to TPR or FPR. When $\alpha$ was increasing, there were less data collections added into $\mathbb{E}_N$. Thus the update of $\mathbb{E}_N$ became slower and FPR went higher. On the contrary, TPR became higher as $\alpha$ increased. Moreover, since $|\mathbb{E}_N| > |\mathbb{E}_A|$, it needs more collection instances for $|\mathbb{E}_N|$ then that for $|\mathbb{E}_A|$ to keep up to the trend. Therefore, it was faster of FPR to increase than that of TPR. As a result of that, there were more false alarms emerged and ACC went lower, as $\alpha$ increased from 0.1 to 0.5. After that, however, although FPR was still increasing, total number of normal instances decreased dramatically and those false alarms contributed less to total errors. Therefore, ACC rose up again. \textcolor{red}{present tense! Throughout the experiment section, the problem is always. You should know when to use past and when present!}

@@

			In Fig.~\ref{fig:roc-magnitude}, we test the classifier with different magnitude of centralised click farming. In former experiments, $\nu = 1$. If $\nu $ is smaller, then it will be harder for the classifier to identify anomalous data collections since the anomalous distribution will be closer to normal ones. It can be concluded from the figure that the 1st level classifier can be efficient even when $\nu = 0.3$. However the 2nd level classifier is less sensitive. That is because the 1st level histogram provides more probability entries than 2nd level histograms do. Data collections are compressed from 1st to 2nd level. But for real world click farming behaviours (usually, $\nu > 1$) both classifiers can be efficient enough.

@@

			We test those calculators on synthetic data set with $\alpha = 0.1, \nu = 1$. After having tested each level of classifier and each type of anomalies, we got 4 F1 scores and added them up. Equation 5 gives best performance. Then those equations were tested on large amount of gaussian distributed data instances. 90K and 10K data points were sampled from 500 pairs of random gaussian distributions which represent normal and anomalous distributions respectively, yielding 500 F1 scores for each equation. We compared the average score and discovered that equation 9 gives the best result.

			Equation 9 gives best classification result for two gaussian distributions but does not outperform others in real world data. Part of the reasons are mentioned in section~\ref{sec:alg-threshold}. Another reason is that the size of evidence sets are too small, that the gaussian distribution may not be well approximated.

		\subsection{Comparison: Multinomial Goodness-of-Fit}
			There has been few research on collective anomaly from the aspect of data collection distribution. In 2011, Wang et. al had proposed a technique, \textit{Multinomial Goodness-of-Fit}(MGoF), to analyze likelihood ratio of distributions via Kullback-Leibler divergence which is indeed a hypothesis test on distributions~\cite{wang2011statistical}. The following experiments were performed on the synthetic data sets by MGoF, providing the comparison baseline of our approach.

			We first tested performance of MGoF with different $\alpha$'s. Here $T$ is set to the point correspond to 0.95 in chi-square cumulative distribution function, and $c_{th}$ is set to 10. For simplicity, we only tested on 1st level classification against centralized click farming and 2nd level classification against equalized click farming. 
			The results are shown in TABLE~\ref{tab:mgof}.

@@

		\begin{figure}[!t]
			\centering
			\includegraphics[width=0.49\linewidth]{fig/ROC-Alpha-MGOF.png}
			\includegraphics[width=0.49\linewidth]{fig/ROC-Nu-MGOF.png}
			\caption{These two diagrams show the ROC curve of MGoF with same parameters in the former experiment. Results were generated by classifying against centralized click farmed data via 1st level histograms. By adopting different $\alpha$'s and $\nu$'s, we can find that the classifier is not so sensitive as that provided in our technique.}
			\label{fig:roc-mgof}
		\end{figure}

		Left half of the table sees both trends of increasing FPR and ACC. That is because MGoF always classify as anomalous the first $c_{th}$ distributions correspond to certain null hypothesis. Thus when $\alpha$ increases, the proportion of misclassified normal collections also becomes larger. While those anomalies are still considered anomalous. And given that the total number of normal collections drops down, the overall accuracy tends to increase as more instances are correctly classified as anomalous. However, the right half shows a different trend. The basic reason is that MGoF uses KLD instead of JSD. In the Taobao dataset, the discrete estimation of collect distributions oscillate a lot, leading to many situations that the prerequisite of KLD is unsatisfied. Thus the calculation of KLD may not give a correct measurement. Furthermore, the 2nd histogram provides fewer probability entries than the 1st level does. Thus it shows a more significant deviation from our expectation. Another reason that it shows highly unstable trends is that it simply adopts a threshold which is relative only to the hypothesis of normal data. The threshold value requires lots of observation and tuning and still may not be adaptive to most of the circumstances.

		Another main drawback of MGoF is that its learning procedure of anomalous probability hypothesis is inefficient. To maintain a comprehensive knowledge of the behaviour of anomalies, MGoF has to reserve a single hypothesis entry for every type of them. But in reality, it is always the case that we face the heterogeneity of outliers. However in our technique, that is not a problem since it can map and gather all anomalies together and draw a universal boundary between them and all normal collections.

		Fig.~\ref{fig:roc-mgof} shows two ROC curves as comparisons with those in Fig.~\ref{fig:roc-alpha} and~\ref{fig:roc-magnitude}. For classifiers in MGoF, they are vulnerable to a high error rate. While our technique outperforms at any proportion of click farmed data and also more efficient. For a relatively small magnitude of click farming, the classifier of MGoF quickly breaks down and degraded to be trivial. On the contrary, our techniques provides classifier sensitive enough even toward a relatively small magnitude of click farming.

>>>>

		It is hard to detect a single record that is alerted but still remain in correct value scopes, but if many data records are altered to change a final decision, we can still detect malicious data manipulation behaviours.
		According to our observation, typical manipulations on numerical data will lead to a drift or distortion of its original distribution. For measurable reshaping, we can enclose data collections with similar distribution patterns and filter out those strangely shaped ones. 
		To address problems caused by data manipulation, we propose a novel technique which sorts out manipulated data collections from normal ones by adopting statistical distance.
		In this paper, we focus on a concrete data manipulation problem: click farming in online shops, and try to apply our technique to pick out those dishonest sellers.
		We use Jensen-Shannon divergence as the similarity measurement among different distributions. Comparing with an estimated ground truth, each data collection can be mapped into a single real number within a definite interval. Then a gaussian classifier can be applied to detect outliers derived from manipulated data. To automatically calculate adaptive threshold for the classifier, we keep two evidence sets for both normal points and anomalies, taking advantage of the property provided by Jensen-Shannon divergence.
		In the dynamic environments, these evidence sets are modified after every data collection is checked, in which manner they act intuitively as slide windows and keep up to the evolving features in dynamic scenarios.
		Our contribution includes: 1) A brief review on data anomaly detection and a study on the problem of click farming; 2) Detailed description of both basic and dynamic framework of our technique, resolving several technical difficulties of distribution estimation and automated adaptive threshold; 3) Real world data experiments that test efficiency of our technique and a comparison with a previous work on the same topic.
		%The details of our technique are put together with a real world problem of ``Click Farming'' and had been evaluated on both raw and synthetic data sets corresponding to the problem, demonstrating the correctness and effectiveness of the technique.

@@

			Detection approaches can be categorized into three types according to whether data is labeled: \textit{supervised}, \textit{semi-supervised} and \textit{unsupervised} anomaly detection. As the name suggests, supervised detection methods train models on completely labeled data, while unsupervised detection leverages data without any labeling. Semi-supervised detection approaches train model on data that has labeled instances for only the normal class. Supervised detection is commonly applied when both normal and anomalous data can be obtained~\cite{fujimaki2005approach}. When it comes to the circumstances that anomalous data is hard to obtain or there exist too many types of anomalies to enumerate, semi-supervised or unsupervised approaches are usually taken into consideration.
			To make the final decision, detection algorithms mostly yield a score from each input instance, denoting how likely it is anomalous. An algorithm then selects top few as anomalies or compare the scores with a threshold, or outputs a label on each instance, and then decides whether each label belongs to the normal class.
			Currently, distance based~\cite{cao2014scalable,cao2017multi} and feature evolving algorithms~\cite{masud2013classification,li2015discovery,shao2014prototype} catch most attention. Others adopted tree isolation~\cite{zhang2017lshiforest}, model based~\cite{yin2016model} and statistical methods~\cite{zhu2002statstream} in certain applications.

@@

			A research performed in China showed that 81.9\% of investigated people had heard of the behaviour of click farming, 51.2\% are aware of click farm and 18.9\% of them had experience of click farming themselves~\cite{yan2015report}. American researchers reported in 2015 that over 11000 sellers on Taobao were detected to have click farmed records and only 2.2\% of 4000 investigaed dishonest sellers had been penalized because of the cheating attempts~\cite{netease2015research}.

@@

			\begin{figure}[t]
				\centering
				\includegraphics[width=\linewidth]{fig/ExampleCDF.png}
				\caption{Example cumulative distribution function of original and click farmed daily transaction data}
				\label{fig:example-ecdf}
			\end{figure}

@@

	\section{Preliminaries}\label{sec:preliminaries}
		Statistical divergence, also called statistical distance, measures the similarity between two or more distributions.
		Mathematically, statistical divergence is a function which describes the ``distance'' of one probability distribution to the other on a statistical manifold. Let $\mathbb{S}$ be a space of probability distributions, then a divergence is a function from $\mathbb{S}$ to non-negative real numbers: 
		\begin{equation}
			D(\cdot || \cdot): \mathbb{S} \times \mathbb{S} \rightarrow \mathbb{R^+} \cup \{0\}
		\end{equation}

@@

	\section{Statistical Detection}\label{sec:algorithm-details}
		Diverse data sets in the real world show certain structures caused by hidden patterns or relationships among records. For example, traffic volume in the highway and the business transaction records, they may show a relatively stable distribution in the daily scale. Manipulation on those data (e.g. Fig.~\ref{fig:example-ecdf}) results in a drift or distortion of the distribution, which can be captured to trigger an alarm. There are some difficulties in the specific design and implementation of the technique:

@@

			In order to generate an accurate approximation, the step size is the most important parameter the algorithm should determine. If the size is too small then the histogram will be over fitting; but if the size is too large then the estimation will be too coarse to depict the original shape. According to statistics theory, when dealing with a sample size of $k$, a step size of 
			\begin{equation}\label{equ:step-size}
				l = c \sigma k^{-0.2},
			\end{equation}
			will give a best partition size, where $c$ is a constant relative to the shape of distribution (e.g. for normal distribution, $c=1.05$). For data sets with a large number of elements, a random sampling method, such as Monte-Carlo method, can be applied to speed up the estimation procedure.

@@

			A naive but prevalent approach is to set a fixed value as the threshold. This approach is easy to implement and may give satisfying results in specific cases. However, a fixed threshold requires specific analysis in the certain scenario, manual observation and tuning of parameters, which involves lots of human labour. The rule of ``$3 \sigma$'' declares all instances outside $[\mu - 3\sigma, \mu + 3\sigma]$ to be anomalous. It can be used to automatically determine a threshold. But as a rigid metric, it is merely an estimation of a suitable boundary considering average situations, which is far from optimality when concrete data is provided. It would be either higher than the optimum if anomalous data lies far away from the normal cluster, or lower than the optimum if the anomalies sit close to the cluster centre.

@@

			Fortunately, applying divergence as the distance measurement among data collections provides a fine property. That is, divergences of normal data collections assemble together, forming a quasi-gaussian distribution. And those of anomalies also form a quasi-guassian distribution which lies in the right-hand-side to the other one on the real line. As a result of further observation, however, true distribution of both JSDs derived from normal and anomalous data collections may differ a little more from the standard gaussian than the expected estimation error (Fig.~\ref{fig:jsd-dist}). That is due to the unknown randomness within real world data. Few assumptions can be applied in real world data sets, no mention that data volume is sometimes relatively low. This topic is out of the domain discussed in this paper and we here only introduce the technique instead of the specific distribution model. 
			Certainly, if stronger assumptions can be included to provide a more precise model, this component in the framework can be replaced to give better results.
			For the simplicity of our proposal, we deem the distributions of JSDs to be gaussian.

@@

			According to E.q.(\ref{equ:linear-weight}), the threshold value can be automatically determined. The optimal threshold will minimize total errors and yield an optimal outcome. Another evidence set is thus required for estimating $PDF_a(x)$.

			However, this is not accurate enough, since E.q.(\ref{equ:linear-weight}) implicates an assumption that the chances are the same for a new data collection to be either anomalous or not. If we can determine the probability for a new data collection to be anomalous in any segment of data sequence, the equation should be modified as:
			\begin{equation}\label{equ:linear-balanced}
				{\footnotesize
				\begin{split}
					T & = \mathop{\arg\min}_{T} \alpha\int_{0}^{T}PDF_{a}(x)dx +
					(1-\alpha)\int_{T}^{log_k2}PDF_{n}(x)dx\\
					& \approx \mathop{\arg\min}_{T}
					\alpha\int_{0}^{T}
					\frac{e^{-\frac{(x - \mu_a)^2}{2\sigma_a^2}}}{\sqrt{2\pi} \sigma_a}dx
					+ 
					(1-\alpha)\int_{T}^{log_k2}
					\frac{e^{-\frac{(x - \mu_n)^2}{2\sigma_n^2}}}{\sqrt{2\pi} \sigma_n}dx
				\end{split}}
			\end{equation}

			Where $\alpha$ is the anomaly probability. E.q.(\ref{equ:linear-balanced}) is much more complicated. But it can be reduced to a quadratic equation.
			Section~\ref{sec:exp-threshold} compares some estimations for optimal threshold under a real world circumstance. It shows the difference among calculators and that E.q.(\ref{equ:linear-balanced}) outperforms others when $PDF_n(x)$ and $PDF_a(x)$ are actually gaussian.

		\subsection{Dynamic Detection}\label{sec:alg-dynamic}
			Algorithm~\ref{alg:static} regards every data collection to be sampled from a static environment. That is to say the seller will never change his or her products and customer volumes always remain the same. In most cases, real world data is always in the process of evolution and fluctuation. Online shops are often in the process of expanding or dwindling. Thus the sales distribution will slightly change as time goes on. Therefore, the algorithms should automatically adapt to the trend at any time. To meet the need, a sliding window technique has been applied to the basic algorithm frame work. Thus, considering discussion in section~\ref{sec:alg-histogram} and~\ref{sec:alg-threshold}, a dynamic version is proposed in Algorithm~\ref{alg:dynamic}.

@@

		\begin{enumerate}
			\item How to emulate different types of click farming?
			\item Is the analysis in section~\ref{sec:related-realworld} and~\ref{sec:alg-basic} applicable and accurate in real world data sets?
			\item Is the technique efficient against click farming? And How sensitive will the classifier be confronting different magnitude of click farming?
			\item What is the performance of different adaptive thresholds?
		\end{enumerate}

@@

			Fig.~\ref{fig:daily-transaction-volume} shows the daily transaction volume of the seller. It sees a trend of daily sale which is slightly moving as the time goes. And the daily selling distributions, as is shown in Fig.~\ref{fig:sale-distribution-sample}, display a roughly similar shape with each other.

@@

			To play the role of purchasing platform, we surveillance two levels of transaction distribution. The first level is to simply draw a histogram aligned to time spans. The second level is to draw a histogram on the sub-volumes in each time span. For example, as shown in Fig.~\ref{fig:histogram-example}, the first level histogram can be drawn by counting the number of hourly sales. The frequencies of each bucket in 1st level histogram is: $\mathbb{F}=$\{0, 0, 0, 0, 0, 0, 0, 1, 13, 30, 37, 68, 60, 66, 72, 94, 75, 113, 127, 182, 165, 61, 0, 0\}. Then, counting $\mathbb{F}$ with a step size 20 gives the 2nd level histogram.

@@

			In order to test the performance of Algorithm~\ref{alg:dynamic}, every single collection was fed into the algorithm by time order. Each input collection has a probability of $\alpha$ to be anomalous, namely, click farmed. The algorithm checked each collection with 1st or 2nd level histogram and gave an answer of true or false. Several metrics are explored in the following experiments.

@@

			When classifying toward 1st level histograms, centralized click farming behaviours can be easily discovered. As displayed in the left two columns in Fig.~\ref{fig:raw-hist-1st}, normal collections share a similar distribution while centralized click-farmed ones abruptly violates the original shape. However, as a clever click farmer, equalized click farming did not in the least distort the distribution. Most of them escape the check under perfect disguises.
			But when it comes to 2nd level histograms, the ``clever disguise'' does not work any longer. It can be clearly seen in Fig.~\ref{fig:raw-hist-2nd} that both types of click farming shows an obvious difference from the normal ones, while the normal ones still share a similar distribution.
			From the overview in Fig.~\ref{fig:raw-overview}, the difference between normal and anomalous collections can be observed more intuitively.

		\subsection{Experiment on Synthetic Data}\label{sec:exp-synthetic}
			As is put in the former section, every single record in transaction collections gives only a time stamp aligned at hours. Part of the information was erased with the absence of minutes and seconds. In the following experiments, every time stamp was assigned a random value for minutes and seconds. Therefore, the synthetic data set should be closer to the real world case. Moreover, the step size in the histograms can now be calculated more precisely. In the 1st level histogram, the constant $c$ in E.q.(\ref{equ:step-size}) was set to 0.5 since the PDF of daily distribution was approximately a linear function. And in the 2nd level histogram, sub-volumes of every 300 seconds were counted, producing more data points in the 2nd level data collections. Then, constant $c$ in E.q.(\ref{equ:step-size}) was also set to 0.5.
			We tested algorithm performance for $\alpha \in \{0.1, 0.3, 0.5, 0.7, 0.9\}$, with $\mathbb{E}_N$ and $\mathbb{E}_A$ the same configuration as before. Results are shown in Table~\ref{tab:syn-result-1st} and~\ref{tab:syn-result-2nd}.

@@

			The result shows that the algorithm can efficiently distinguish the normal and anomalous data collections. No matter how much proportion in them is anomalous, the algorithm always gives a high accuracy. That is because the adaptive threshold is designed to minimize the number of total errors, which is not relevant directly to TPR or FPR. When $\alpha$ is increasing, there are less data collections added into $\mathbb{E}_N$. Thus the update of $\mathbb{E}_N$ becomes slower and FPR goes higher. On the contrary, TPR becomes higher as $\alpha$ increases. Since $|\mathbb{E}_N| > |\mathbb{E}_A|$, it needs more collection instances for $|\mathbb{E}_N|$ then that for $|\mathbb{E}_A|$ to keep up to the trend. Therefore, it is faster of FPR to increase than that of TPR. As a result of that, there are more false alarms emerged and ACC drops lower, when $\alpha$ increases from 0.1 to 0.5. After that, however, although FPR is still increasing, total number of normal instances decreases dramatically and those false alarms contribute less to total errors. Therefore, ACC rises up again.

@@

			In Fig.~\ref{fig:roc-magnitude}, we test the classifier with different magnitude of centralised click farming. In former experiments, $\nu = 1$. If $\nu $ is smaller, then it will be harder for the classifier to identify anomalous data collections since the anomalous distribution will be closer to normal ones. It can be concluded from the figure that the 1st level classifier can be efficient even when $\nu = 0.3$. However the 2nd level classifier is less sensitive. That is because the 1st level histogram provides more probability entries than the 2nd level histograms does. Data collections are compressed from 1st to 2nd level. For real world click farming behaviours (usually, $\nu > 1$) both classifiers can be efficient enough.

@@

			We test those calculators on synthetic data set with $\alpha = 0.1, \nu = 1$. After having tested each level of classifier and each type of anomalies, we got 4 F1 scores and added them up. E.q.(5) gives best performance. Then those equations were tested on large amount of gaussian distributed data instances. 90K and 10K data points were sampled from 500 pairs of random gaussian distributions which represent normal and anomalous distributions respectively, yielding 500 F1 scores for each equation. We compared the average score and discovered that E.q.(9) gives the best result.

			E.q.(9) gives best classification result for two gaussian distributions but does not outperform others in real world data. Part of the reasons are mentioned in section~\ref{sec:alg-threshold}. Another reason is that the size of evidence sets are too small, that the gaussian distribution may not be well approximated.

		\subsection{Comparison: Multinomial Goodness-of-Fit}
			Wang et. al proposed a technique, \textit{Multinomial Goodness-of-Fit} (MGoF), to analyze likelihood ratio of distributions via Kullback-Leibler divergence, and is fundamentally a hypothesis test on distributions~\cite{wang2011statistical}. 
			MGoF divides the observed data sequence into several windows. It quantizes data in each window into a histogram and check these estimated distributions against several hypothesis. If the target distribution rejects all provided hypothesis, it is considered an anomaly and preserved as a new candidate of null hypothesis. If the target distribution failed to reject some hypothesis, then it is considered a supporting evidence of the one that yields most similarity. Furthermore, if the number of supporting evidence is larger than a threshold $c_{th}$, it is classified as non-anomaly.

			MGoF is the best competitor out of the similar techniques, and we use it as our baseline against our approach. The following experiments were performed on the synthetic data sets for MGoF.

			We first tested performance of MGoF with different $\alpha$'s. Here $T$ is set to the point corresponding to 0.95 in chi-square cumulative distribution function, and $c_{th}$ is set to 10. For simplicity, we only tested on 1st level classification against centralized click farming and 2nd level classification against equalized click farming. 
			The results are shown in TABLE~\ref{tab:mgof}.

@@

		\begin{figure}[!t]
			\centering
			\includegraphics[width=0.49\linewidth]{fig/ROC-Alpha-MGOF.png}
			\includegraphics[width=0.49\linewidth]{fig/ROC-Nu-MGOF.png}
			\caption{These two diagrams show the ROC curve of MGoF with same parameters. The results were generated by classifying against centralized click-farmed data via 1st level histograms. By adopting different $\alpha$'s and $\nu$'s, we can find that the classifier is not so sensitive as provided in our technique.}
			\label{fig:roc-mgof}
		\end{figure}

		The left half of the table shows both trends of increasing FPR and ACC. That is because MGoF always classifies as anomalous the first $c_{th}$ distributions supporting every null hypothesis. Thus when $\alpha$ increases, the proportion of misclassified normal collections also becomes larger, while those anomalies are still considered anomalous. And given that the total number of normal collections drops down, the overall accuracy tends to increase as more instances are correctly classified as anomalous. However, the right half shows a different trend. One reason is that MGoF uses KLD other than JSD. In the Taobao dataset, the discrete estimation of distributions oscillates a lot, leading to that the prerequisite of KLD is often unsatisfied. Thus the calculation of KLD may not give a correct measurement. Furthermore, the 2nd histogram provides fewer probability entries than the 1st level does. Thus it shows a more significant deviation from our expectation.

		%\textcolor{green}{The other reason why it shows highly unstable is that it simply adopts a threshold, which is relative only to the hypothesis of normal data. The threshold value requires lots of observation and tuning, and may not be adaptive to most of the circumstances.}

		MGoF's learning procedure of anomalous probability hypothesis is inefficient. To maintain a comprehensive knowledge of anomalies, MGoF has to reserve a single hypothesis entry for every type of them. But in reality, it is always the case that we face the heterogeneity of outliers. In the Taobao's data set, there can be tens of anomalous distribution caused solely by centralized click farming. It takes a long time to discover every possible type of anomaly. Besides, if there happens to be more than $c_{th}$ anomalous distributions of the same type, later discovered collections will no longer declared to be anomalous any more.
		However, in our technique, that is not a problem since it can map and gather all anomalies together and draw a universal boundary between them and all normal collections.

		Fig.~\ref{fig:roc-mgof} shows two ROC curves as comparisons with those in Fig.~\ref{fig:roc-alpha} and~\ref{fig:roc-magnitude}. For the classifiers of MGoF, they  compromise to a high error rate. Because more anomalies gathered together and the algorithm recognizes them as clusters of normal data.
		For a relatively small magnitude of click farming, the classifiers of MGoF quickly degrade to be trivial. The rigid threshold cannot automatically rise up and is thus much lower to optimal.
